---
title: "Wordcloud-Script"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

R script to create wordcloud from text document, using the `wordcloud2` package. 

## Example
Here is an example of how to create a wordcloud. I use my PhD thesis as the example text. My PhD thesis can be found at:
<https://www.researchgate.net/publication/319876899_Corporate_networks_of_international_investment_and_trade>

First, Iload the relevant libraries:
```{r LIB,eval=FALSE}
library(tm)
library(magrittr)
#library(devtools)
#devtools::install_github("lchiffon/wordcloud2")
library(wordcloud2)
```

Then I save the document as a .txt file and then read into R:

```{r Read,eval=FALSE}
text1<-"C:\\Users\\example.txt"
text2 <-readLines(text1)
DOCtxt<-Corpus(VectorSource(text2))
```

I then clean the document, removing whitespace, common words and numbers. I convert all words to lowercase. And finally, I remove a list of words - these are common words for this particular document:

```{r remove,eval=FALSE}
DOCtxt_data<-tm_map(DOCtxt,stripWhitespace)%>%tm_map(.,tolower)%>%
  tm_map(.,removeNumbers)%>%tm_map(.,removePunctuation)%>%
  tm_map(.,removeWords,stopwords("english"))%>%
  tm_map(.,removeWords,"course")
  tm_map(.,removeWords,c("and","the","our","that","table","figure",
                         "for","are","also","more","has",
                         "must","have","should","this",
                         "with","furthermore","PhD",
                         "additionally","in","number",
                         "which","patterns","use","one",
                         "approach","whether","capture",
                         "effects","specifically",
                         "instance","yet","two",
                         "rather","approaches","along",
                         "however","extent","provides",
                         "applied","characterised",
                         "amongst","need","often","order",
                         "table","based","key","examining",
                         "captures","important","positive","using",
                         "negative","better","perspective","journal",
                         "case","therefore","can","work","et","al",
                         "used","role","set","studies","measures",
                         "paper","provide","figures","tables"))
```

From this - we create an object providing words and frequency:
```{r DTM,eval=FALSE}
dtm<- TermDocumentMatrix(DOCtxt_data)%>%as.matrix()
v <- sort(rowSums(dtm),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
```

## Wordcloud Plot
Now I have the clean object, I can create the plots. 

### Wordcloud plot:
```{r WC_command,eval=FALSE}
wordcloud2(d)
```
  
```{r WC, echo=FALSE}
library(NLP)
library(tm)
library(magrittr)
speech <-"C:\\Users\\matt_\\Documents\\Wordcloud\\CORPORATE NETWORKS OF INTERNATIONAL_WORDCLOUD.txt"
THESIStxt <-readLines(speech)
THESIS<-Corpus(VectorSource(THESIStxt))
THESIS_data2<-tm_map(THESIS,stripWhitespace)%>%tm_map(.,tolower)%>%
  tm_map(.,removeNumbers)%>%tm_map(.,removePunctuation)%>%
  tm_map(.,removeWords,stopwords("english"))%>%
  tm_map(.,removeWords,c("and","the","our","that","table","figure",
                         "for","are","also","more","has",
                         "must","have","should","this",
                         "with","furthermore","PhD",
                         "additionally","in","number",
                         "which","patterns","use","one",
                         "approach","whether","capture",
                         "effects","specifically",
                         "instance","yet","two",
                         "rather","approaches","along",
                         "however","extent","provides",
                         "applied","characterised",
                         "amongst","need","often","order",
                         "table","based","key","examining",
                         "captures","important","positive","using",
                         "negative","better","perspective","journal",
                         "case","therefore","can","work","et","al",
                         "used","role","set","studies","measures",
                         "paper","provide","figures","tables"))

dtm<- TermDocumentMatrix(THESIS_data2)%>%as.matrix()
v <- sort(rowSums(dtm),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
library(wordcloud2)

wordcloud2(d)
```
  

### Letterplot:
```{r LC_command,eval=FALSE}
letterCloud(d, word = "EXAMPLE", color='random-light' , backgroundColor="black")
```
  
  
```{r WL, echo=FALSE}
library(NLP)
library(tm)
library(magrittr)
speech <-"C:\\Users\\matt_\\Documents\\Wordcloud\\CORPORATE NETWORKS OF INTERNATIONAL_WORDCLOUD.txt"
THESIStxt <-readLines(speech)
THESIS<-Corpus(VectorSource(THESIStxt))
THESIS_data2<-tm_map(THESIS,stripWhitespace)%>%tm_map(.,tolower)%>%
  tm_map(.,removeNumbers)%>%tm_map(.,removePunctuation)%>%
  tm_map(.,removeWords,stopwords("english"))%>%
  tm_map(.,removeWords,c("and","the","our","that","table","figure",
                         "for","are","also","more","has",
                         "must","have","should","this",
                         "with","furthermore","PhD",
                         "additionally","in","number",
                         "which","patterns","use","one",
                         "approach","whether","capture",
                         "effects","specifically",
                         "instance","yet","two",
                         "rather","approaches","along",
                         "however","extent","provides",
                         "applied","characterised",
                         "amongst","need","often","order",
                         "table","based","key","examining",
                         "captures","important","positive","using",
                         "negative","better","perspective","journal",
                         "case","therefore","can","work","et","al",
                         "used","role","set","studies","measures",
                         "paper","provide","figures","tables"))

dtm<- TermDocumentMatrix(THESIS_data2)%>%as.matrix()
v <- sort(rowSums(dtm),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
library(wordcloud2)

letterCloud(d, word = "EXAMPLE", color='random-light' , backgroundColor="black")
```